Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2019-11-05 manuscript/climate_sensitivity_draft.Rmd
update word count

text | word count | other | n
---------------------------------------------|---------------------|-----------------------------|--------------------
Total word count (excluding summary, references and legends) |  currently ~6000 (strict limit 6,500)	 |	No. of figures | 	2 (both colour)
Summary|  	## (limit 200) | 	No. of Tables | 	5  
Introduction|	currently ~1536 |	No of Supporting Information files | 	###.
Materials and Methods |	currently ~1442	||	 
Results |	currently ~1437	 ||
Discussion |	currently ~1881 (limit 30% of total (not strict), or 1950 if manuscript reaches word limit)	||
Acknowledgements | 	~75 unwritten	||

>>>>

text | word count | other | n
---------------------------------------------|---------------------|-----------------------------|--------------------
Total word count (excluding summary, references and legends) |  currently ~6442 (strict limit 6,500)	 |	No. of figures | 	2 (both colour)
Summary|  	## (limit 200) | 	No. of Tables | 	5  
Introduction|	currently ~1339 |	No of Supporting Information files | 	###.
Materials and Methods |	currently ~1604	||	 
Results |	currently ~1558	 ||
Discussion |	currently ~1866 (limit 30% of total (not strict), or 1950 if manuscript reaches word limit)	||
Acknowledgements | 	~75 unwritten	||
